% !TEX root = jorge_saldivar.tex

\section{Data Science Projects}

- \cusemph{Motivation Factors and Participation Patterns in Crowdsourcing ($\sim$2k records).} Applied \textbf{exploratory data analysis (EDA)} to study the profile of the participants of crowdsourced civic participation processes. Employed \textbf{non-parametric statistical tests} (Wilcox, Spearman, Chi-square, Kruskal-Wallis, Friedman) to examine change in the motivation factors that drive people to crowdsourced civic participation processes. Used \textbf{Logistic Regression} to predict the odds of participants to stay engaged in crowdsourcing processes. (Tools: R, dplyr, ggplot2)\footnote{Repo: https://github.com/joausaga/finland-experiment-study}

- \cusemph{The effectiveness of Social Sharing Practices ($\sim$35k records).} Used \textbf{Multivariate Linear Regression} and \textbf{parametric statistical tests} (Pearson correlation, T-test) to study the effectiveness of the ubiquitous social media sharing buttons in increasing participation in online social communities (Tools: R, ggplot2, dplyr, reshape)\footnote{Repo: https://github.com/joausaga/ims-sn-study}

- \cusemph{Collective and Individual Behavior in Online Communities ($\sim$300k records).} Used \textbf{K-means algorithm} and \textbf{non-parametric statistical tests} (Chi-square, Kruskal-Wallis) to discover patterns in the collective behavior of online innovation communities (Tools: R, ggplot2, dplyr)\footnote{Repo: https://github.com/joausaga/collective-behavior-im-communities}

- \cusemph{Politic Bots ($\sim$200k records).} Employed \textbf{exploratory data analysis (EDA)} techniques (summary statistics and visualizations) to understand how social media bots and fake accounts are used to promote and manipulate information during electoral periods (Tools: Python, Pandas, Numpy, Matplot, MongoDB)\footnote{Repo: https://github.com/ParticipaPY/politic-bots}

%- \cusemph{UTurn.} Used \textbf{non-parametric Spearman} correlation to examine the sense of presence, perspective-taking and usability of a split sphere, first-person perspective 360\degree video (Tools: R, dyplr)\footnote{Repo: https://github.com/joausaga/uturn}

%- \cusemph{Improving Asuncion's Open Street Map ($\sim$450k records).} Employed data munging techniques to assess the quality of Asuncion's Open Street Map for validity, accuracy, completeness, consistency, and uniformity (Tools: Python, MongoDB, ElementTree XML)\footnote{Repo: https://github.com/joausaga/openstreetmap}

- \cusemph{Online Popularity of Movies ($\sim$10k records).} Used \textbf{exploratory data analysis (EDA)} methods (summary statistics, visualizations, and correlation) to understand the factors that contribute to the online popularity of movies (Tools: Python, Pandas, Numpy, Matplot)\footnote{Repo: https://github.com/joausaga/moviesonlinepopularity}


