% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[spanish]{babel}
\usepackage[latin1]{inputenc}
\usepackage{url}


\begin{document}

\name{Jorge Saldivar}
% \address used twice to have two lines of address

%\address{Tte. Cantaluppi y G. Molinas, Asunci\'on, Paraguay}
\address{jorgesaldivar@gmail.com}
\address{\url{www.jorgesaldivargalli.com}}

\begin{resume}
 
%\section{OBJECTIVE} Position in Datumize. 
\small{Ph.D. candidate at the Department of Information Engineering and Computer Science, University of Trento (Italy) and assistant researcher at the Department of Electronic and Informatics of the Catholic University (Paraguay), where I participate in the investigation and development of tools that empower citizens in public decision-making and innovation processes. My research interests include crowdsourcing, collective intelligence, and civic engagement}.

\section{CURRENT POSITION}
{\sl Assistant Researcher} \hfill \\
Department of Electronic and Informatics, Catholic University of Asunci\'on, Paraguay.
\begin{itemize}  \itemsep -2pt %reduce space between items
\item Research, modelling, design and implementation of IT applications and services that support and facilitate the participation of Paraguayan citizens in innovating public services.
\end{itemize}
 
\section{EDUCATION} 
	{\sl PhD candidate,} Information and Communication Technology,\\ 
ICT Doctoral School, University of Trento, Italy (expected, April 2016).\\
	{\bf Thesis:} \emph{Integrating Platform for Eliciting Ideas with Social Network: An approach to empower civic engagement for public sector innovation}.
                
	{\sl Bachelor of Science (B.Sc.),} Informatics Engineering,\\ 
    Catholic University "Nuestra Se\~nora de la Asunci\'on", Paraguay, 2010.\\
    {\bf Thesis:} \emph{Improving cooperative and competitive behaviors on visually impaired children}.
 
 
%\section{SOCIAL IMPACT RESEARCH PROJECTS}
\section{COLLABORATION IN RESEARCH PROJECTS}
	{\sl Participa.PY:} Developing ICT solutions to empower citizens to collaborate in the co-creation of social impact solutions and public sector innovations. (Technical Leader)
	
	{\sl Civic CrowdAnalytics:} Designing machine learning-based tools to automatically analyze and synthesize crowdsourced civic input.
	
	{\sl The California Report Card:} Implementing mobile-based solutions to structure and streamline communication from the California residents to their elected officials.

	{\sl The Finnish Experiment:} Analyzing participation patterns and effect of moderation actions in crowdsourced policy-making processes.
	
	%{\sl Social Ideation:} Develop of a tool that aims at harvesting the expertise, knowledge, and opinions of today's biggest virtual communities -- the social networks -- to enrich and complement citizen-sourcing open innovation processes.
	
	{\sl Agora 2.0:} Integrating public displays and open innovation platforms to create a synchronized on-line and on-site system oriented to promote civic participation in discussions about public interest issues.

	%{\sl BPM4People:} Develop methodologies, techniques, and approaches to model and deploy business processes that are executed collaboratively by people in social networks.
	
	%{\sl Ianus:} Develop of methods and techniques to perform functional validation of business processes.
		
	%{\sl Club de Othello:} Educational project that seeks for exploiting the expressiveness of multimedia tools to help visually-impaired children in learning spatio-temporal concepts and in improving their social abilities.
 
 
\section{RESEARCH \\ EXPERIENCE}
{\sl Visiting Researcher} \hfill July 2014 - October 2014 \\
Center for Information Technology Research in Interest of the Society (CITRIS), University of California, Berkeley, California, USA.
\begin{itemize}  \itemsep -2pt %reduce space between items
\item Modeled, designed, and implemented a Twitter-based extension for the platform CAFE used in the project California Report Card to engage citizens of California in the collective assessment of timely issues.
\end{itemize}

{\sl Visiting Researcher} \hfill October 2013 - December 2013 \\
Information Analysis Division, Hewlett-Packard (HP) Labs, Palo Alto, California, USA.
\begin{itemize}  \itemsep -2pt %reduce space between items
\item Designed and implemented an web-based interactive analytic tool for conducting real-time visualization of query execution.
\item Developed a recommendation plugin that annotated the query tree with the most interesting results of its execution analysis, which may indicate execution problems and recommend design solutions for problem queries.
\end{itemize}

{\sl Assistant Researcher} \hfill November 2011 - October 2014 \\
EU-funded BPM4People research project and Trento-province-funded Ianus project.
\begin{itemize}  \itemsep -2pt %reduce space between items
\item Researched on methodologies, techniques, and approaches to construct tools for modeling and deploying of business processes that will be executed collaboratively by people in social networks.
\item Modeled, designed and implemented a spreadsheet-based tool for enabling business process (BP) analysts to conduct BP testing tasks, such as writing metrics and assertions, running tests, and designing test report.
\item Designed and executed usability studies.
\end{itemize}


\section{OTHER PROFESSIONAL EXPERIENCES} 
{\sl Software Developer/Head of Educational Technology} \hfill January 2010 - July 2011 \\
NGO Paraguay Educa. 
\begin{itemize}  \itemsep -2pt %reduce space between items
\item Developed and maintenance of Sugar OS apps (Labyrinth, Poll, TamTam).
\item Designed, modeled, implemented and maintained the educational software stack (learning platforms, online libraries, student tracking systems) used by teachers and students in classrooms during the implementation of the project One Laptop per Child (OLPC).
\end{itemize}
 
{\sl Software Developer/Technology Manager} \hfill March 2008 - December 2008 \\
OLPC pilot project, Catholic University "Nuestra Se\~nora de la Asunci\'on" 
\begin{itemize}  \itemsep -2pt %reduce space between items
	\item Mounted and maintained of Unix servers. Set up and configured OLPC XO laptops. 
	\item Developed and customized educational applications for Sugar OS.
\end{itemize} 
     
{\sl Software Developer} \hfill March 2007 - December 2007 \\
Azucarera Iturbe (Sugar Industry)
\begin{itemize}
	\item Developed, tested and maintained a web-based (ruby on rails) business management system (billing, stocking, accounting, freighting, human resources)
\end{itemize} 

\section{TEACHING AND TUTORING ACTIVITIES}
{\sl Teaching Assistant} \hfill February 2015 - September 2015 \\
University of Trento, Italy. 
\begin{itemize}  \itemsep -2pt %reduce space between items
\item Teaching Assistant for the undergraduate course on Web Programming Technologies. The course was focuses on J2EE web technologies (e.g., Servlet, JSP, JSTL, JavaBean) and the work involved mainly the confection of online teaching materials and the preparation of tests.
\end{itemize}
{\sl Master Thesis Co-tutor} \hfill November 2014 - March 2015 \\
University of Trento, Italy.
\begin{itemize}  \itemsep -2pt %reduce space between items
\item Co-tutor of the Master Thesis: Analyzing and Visualizing citizen opinions collected from social networks presented by Shahadat Chowdhury to obtain the Master in Computer Science at the University of Trento, Italy.
\end{itemize}

 
\section{DATA ANALYTICS PROJECTS}
	{\sl Collective and individual behavior in online Idea Management communities:} Analysis of common patterns of behavior that emerge in online communities by using unsupervised learning algorithms.

	{\sl Motivation factors and participation in crowdsourcing for policy-making processes:} Analysis on how collective intelligence impacts processes of policymaking processes using descri.
	
	{\sl Social sharing practices in open innovation:} Study on the effectiveness of current social sharing practices in the context of open innovation processes for civic participation. 
 
\section{COMPUTER AND \\ DATA ANALYSIS \\ SKILLS} 
\begin{itemize} \itemsep -2pt      
\item Languages and Frameworks: Python, Java, Javascript, PHP, SQL, Ruby, C, C++, Bash, $C\sharp$, Ruby on Rails, Yii, ExtJS, Qooxdoo, Drupal, Play, JQuery, Bootstrap, Django.
\item Analysis Methods: Descriptive statistics, correlation analysis, inferential statistics.
\item Machine Learning: Regression, classification, unsupervised learning and recommendation modeling.
\item Data analytic and visualization tools: R, Azure ML, Kettle, Ggplot, D3, Jit. 
%\item {\sl Web-development Frameworks:} 
\item RESTful APIs: Twitter, Google Plus, Facebook, IdeaScale, Google Translator, Google Drive, Google URL shortener.
%\item {\sl Operating Systems:} OSX, Unix, Windows.
\end{itemize}

%\section{ONLINE EDUCATION}  
%\begin{itemize} \itemsep -2pt
%\item Regression Models - Johns Hopkins University (completed with verified certificate)
%\item Getting and Cleaning Data - Johns Hopkins University (completed)
%\item SciWrite - Stanford University (completed)
%\item The Global Business of Sports - University of Pennsylvania (completed)
%\item I Heart Stats: Learning to Love Statistics - NotreDameX (completed 65%)
%\item Statistics: Making Sense of Data - University of Toronto (completed 50\%)
%\item Engaging Citizens: A Game Changer for Development? - The World Bank Group (completed 40\%)
%\item English Grammar and Style - UQx (ongoing)
%\end{itemize}

\section{MOST RELEVANT PUBLICATIONS}
\begin{itemize} \itemsep -2pt 	
	\item T. Aitamurto, H. Landemore, and Jorge Saldivar. \emph{Unmasking the crowd: participants' motivation factors, expectations, and profile in a crowdsourced law reform}. Information, Communication \& Society (2016): 1-22.
	\item J. Saldivar, C. Rodriguez, F. Daniel, F. Casati, and L. Cernuzzi. \emph{On the (in) effectiveness of the share/tweet button: A study in the context of idea management for civic participation}. IEEE Internet Computing (2016).
	\item J. Saldivar, C. Vairetti, C. Rodriguez, F. Daniel, F. Casati, and R. Alarcon. \emph{Analysis and improvement of business process models using spreadsheets}. Information Systems 57 (2016): 1-19.
	\item J. Saldivar, F. Daniel, F. Casati, L. Cernuzzi. \emph{Idea Management in Social Networks: A Study of how to Tap into the Ideas of Facebook Communities}. In Proceedings of the 17th International Conference on Collaboration Technologies and Systems, 2016.
	\item J. Saldivar, M. Baez, C. Rodriguez, G. Convertino, Grzegorz Kowalik. \emph{Idea Management in the Wild: An exploratory study of 166 online communities}. In Proceedings of the 17th International Conference on Collaboration Technologies and Systems, 2016.	
	\item T. Aitamurto, K. Chen, A. Cherif, J. Saldivar, and L. Santana. \emph{Civic CrowdAnalytics: making sense of crowdsourced civic input with big data tools}. In Proceedings of the 20th International Academic Mindtrek Conference, pp. 86-94. ACM, 2016. \textit{\textbf{(Best paper award)}}
	\item T. Aitamurto, J. Saldivar, J. Salminen. \emph{Self-selection in Crowdsourcing Democracy: A Bug or A Future?}. Crowdwork Workshop, ACM Conference on Supporting Groupwork, 2014.
%	\item J. Saldivar, C. Parra, C. Rodriguez, L. Cernuzzi, V. D'Andrea. \emph{Participa: fostering civic participation for public services innovation}. 13th Participatory Design Conference, 2014.
	\item G. Schiavo, M. Milano, J. Saldivar, T. Nasir, M. Zancanaro, G. Convertino. \emph{Agora2.0: Enhancing Civic Participation through a Public Display}. 6th International Conference on Communities and Technologies, 2013.
%	\item J. Saldivar, L. Cernuzzi. \emph{Club de Othello XO: Una Experiencia de Aprendizaje en Ambiente de Interaccion Social}. Congress of Technology Support Disabilities (IBERDISCAP), 2010, Ciudad de Mexico, Mexico.
%	\item L. Cernuzzi, J. Saldivar.\emph{Club de Othello Xo: Una Experiencia de Aprendizaje en Ambiente de Interaccion Social}. Congress of Technology Support Disabilities (IBERDISCAP), 2008, Cartegena, Colombia.
\end{itemize}

%\section{AWARDS}
%\begin{itemize} \itemsep -2pt 
%	\item Best Paper Award. Academic Mindtrek Conference, October 2016. Paper: Civic CrowdAnalytics: making sense of crowdsourced civic input with big data tools.
%	\item PhD student fellowship. University of Trento, Trento, Italy (2011-2014).
%	\item PhD on the move scholarship. Trento RISE Association, Trento, Italy (2013).
%	\item FC-UPM-IB scholarship for post-graduated studies at Universidad Polit\'ecnica de Madrid, Spain (2011).
%	%\item Golden-medal for best graduated student of 2000 class at San Jos\'e High-School, Asuncion, Paraguay (2000).
%\end{itemize}

%\section{EXTRA-CURRICULAR \\ ACTIVITIES}    
%\begin{itemize} \itemsep -2pt      
%	\item Foundation member of the non-for-profit Organization Paraguay Educa.
%    \item Electoral delegate in local and national elections.
%    \item Team coordinator for medium-sized seminars, retreats, talks.
%    \item Member of the directory board of the Pilgrim movement.
%    \item Participant and coordinator of diverse social campaigns, e.g. {\sl Corazones Abiertos, Juventud que se mueve, SerVos}.
%   \item Member of San Jos\'e high-school student association.
%\end{itemize}

\end{resume}
\end{document}







