\cvsection{Awards}

\begin{itemize}
	\item \textbf{Best Paper Award}. Academic Mindtrek Conference, October 2016. Paper: \textit{Civic CrowdAnalytics: making sense of crowdsourced civic input with big data tools}.
	\item \textbf{PhD student fellowship}. University of Trento, Trento, Italy (2011-2014).
	\item \textbf{PhD on the move scholarship}. Trento RISE Association, Trento, Italy (2013).
	%\item FC-UPM-IB scholarship for post-graduated studies at Universidad Polit\'ecnica de Madrid, Spain (2011).
	%\item Golden-medal for best graduated student of 2000 class at San Jos\'e High-School, Asuncion, Paraguay (2000).
\end{itemize}

\cvsection{\large{Collaboration in research communities}}

Reviewed scientific articles and papers for the following conferences and journals\\

\begin{itemize}
\item \textbf{Conferences:}\\
\textbf{WWW} (Int. Conf. on World Wide Web), \textbf{ISOC} (Int. Conf. on Service Oriented Computing),
\textbf{CTS} (Int. Conf. on Collaboration Technologies and Systems), \textbf{Academic Mindtrek} (Int. Academic Mindtrek Conference), \textbf{ICEIS} (Int. Conf. on Enterprise Information Systems), 

\item \textbf{Journals:}\\
\textbf{JSMO} (Journal of Social Media for Organization)
\end{itemize}

\cvsection{Languages}
\cvskill{Spanish (native speaker)}{5}
\cvskill{English}{5}
\cvskill{Italian}{3}
\cvskill{Portuguese}{2}


\cvsection{Referees}
% \cvref{name}{email}{mailing address}
\cvref{Prof.\ Fabio Casati}{fabio.casati@unitn.it}
{University of Trento, Trento, Italy}

\divider

\cvref{Dr.\ Gregorio Convertino}{gconvertino@informatica.com}
{Informatica Corporation, Redwood City, CA, USA}
