% !TEX root = jorge_saldivar.tex

\section{Recent\\Publications}

\cusemph{Journal Articles}

\textit{Jorge Saldivar}, Cristhian Parra, Marcelo Alcaraz, Rebeca Arteta, and Luca Cernuzzi. ``Civic Technology for Social Innovation: A Systematic Literature Review.'' In \textit{Computer Supported Cooperative Work (CSCW) Journal, pp. 1-39}, Springer, 2018.

\textit{Jorge Saldivar}, Carlos Rodriguez, Florian Daniel, Fabio Casati, and Luca Cernuzzi. ``On the (in)effectiveness of the Share/Tweet button: A study in the context of idea management for civic participation.'' In \textit{IEEE Internet Computing, vol. 21, issue 5, pp. 38-47}, IEEE, 2017.

Tanja Aitamurto, Hélène Landemore, and \textit{Jorge Saldivar}. ``Unmasking the crowd: participants’ motivation factors, expectations, and profile in a crowdsourced law reform.'' In \textit{Information, Communication \& Society, pp. 1-22}, 2016.

\textit{Jorge Saldivar}, Carla Vairetti, Carlos Rodríguez, Florian Daniel, Fabio Casati, and Rosa Alarcón. ``Analysis and improvement of business process models using spreadsheets''. In \textit{Information Systems 57: 1-19}, Elsevier, 2015.

\cusemph{Conference Papers}

Tanja Aitamurto, Shuo Zhou, Sukolsak Sakshuwong, \textit{Jorge Saldivar}, Yasamin Sadeghi, Amy Tran, and Nathalie Mathe. ``Sense of Presence, Attitude Change, Perspective-Taking and Usability in First-Person Split-Sphere 360\degree Video''. In \textit{Proceedings of the 2018 CHI Conference}, ACM, 2018 (to be presented).

Tanja Aitamurto and \textit{Jorge Saldivar}. ``Motivating Participation in Crowdsourced Policymaking: The Interplay of Epistemic and Interactive Aspects''. \textit{Proceedings of the ACM Human-Computer Interaction (CSCW), vol. 1, no. 2, article 18,}, ACM, 2017.

Tanja Aitamurto and \textit{Jorge Saldivar}. ``Examining the Quality of Crowdsourced Deliberation: Respect, Reciprocity and Lack of Common-Good Orientation''. In \textit{Proceedings of the 2017 CHI Conference Extended Abstracts on Human Factors in Computing Systems, pp. 2314-2321}, ACM, 2017.

\textit{Jorge Saldivar}, Marcos Báez, Carlos Rodríguez, Gregorio Convertino, and Grzegorz Kowalik. ``Idea Management Communities in the Wild: An exploratory study of 166 online communities''. In \textit{Proceedings of the 17th International Conference on Collaboration Technologies and Systems (CTS), pp. 81-89}, IEEE, 2016.

\textit{Jorge Saldivar}, Florian Daniel, Fabio Casati, and Luca Cernuzzi. ``Idea Management in Social Networks: A Study of how to Tap into the Ideas of Facebook Communities''. In \textit{Proceedings of the 17th International Conference on Collaboration Technologies and Systems (CTS), pp. 3-10}, IEEE, 2016.

Tanja Aitamurto, Kaiping Chen, Ahmed Cherif, \textit{Jorge Saldivar}, and Luis Santana. ``Civic CrowdAnalytics: Making sense of crowdsourced civic input with big data tools''. In \textit{Proceedings of the 20th International Academic Mindtrek Conference, pp. 86-94}, ACM, 2016

Tanja Aitamurto, \textit{Jorge Saldivar}, and Juho Salminen. ``Self-selection In Crowdsourced Democracy: A Bug Or A Feature?''. In \textit{GROUP Conference}, ACM, 2014.

\textit{Jorge Saldivar}, Cristhian Parra, Carlos Rodríguez, Luca Cernuzzi, and Vincenzo D’Andrea. ``Participa: Fostering civic participation for public services innovation''. In \textit{13th Participatory Design Conference}, 2014.

Gianluca Schiavo, Marco Milano, \textit{Jorge Saldivar}, Tooba Nasir, Massimo Zancanaro, and Gregorio Convertino. ``Agora 2.0: Enhancing civic participation through a public display''. In \textit{Proceedings of the 6th International Conference on Communities and Technologies (C\&T), pp. 46-54}, ACM, 2013.

%Please refer to \url{http://me.jorgesaldivargalli.com/publications} for the complete list of my publications